---
title: "fars_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(courserafars)
```


--- Welcome to the 'fars' package!

`fars_summarize_years` function summarizes the number of accidents by month and year
The function `fars_map_state` plots the accidents location by state and year.
The other functions:
* fars_read
* make_filename
* fars_read_years
are auxiliary functions to the main functions. For more information about them, please check the help files.


*Let's start!*

Here are the packages that you will need to install in advance:
```{r, echo=TRUE, include=TRUE}
library(dplyr)
library(maps)
library(readr)
library(tidyr)
```

## Load the data do your current working directory

To use `fars_map_state`, you need data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. You can download the data [here](https://www.coursera.org/learn/r-packages/peer/25XGp/documenting-code).

Not sure what is your current working directory?

* Type `getwd()` on the console to find out!

## Use fars_summarize_years!

Say you want to know the number of accidents per year and month, then `fars_summarize_year` is your function!

## Use fars_map_state!

Say you want to know the the location of the accidents that occurred in 2013 in the state of California.
Then, the function will take as input, 6 (California state number) and 2013 (the year).

And that's a wrap!
For more details, please check the help files!



